Bayesian exponential random graph modeling of KWL Burial network

### 2020-10-08 analysis/paper/paper.Rmd
tried other parameters and changed object names

<!--burial study- network analysis-->
Burials provide valuable information about past human behavior that can reflect not only the personal life and status of the deceased, but also the expressions of their descendants through grave goods and arrangements [@Pearson1999]. Mortuary practices such as burial forms, grave goods, and related ritual practices could represent the social relations between individuals and allow archaeologists to infer social structures. This enables the study of social differences based on burials to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For examples, grave goods can reflect consumption patterns and social practices in a broader of cultural contexts involves personal identity or social relation through trade, exchange, and gifting [@Coward2013, pp. 252]. The correlation between burials could be viewed as an indicator of social relationship in a society. One way to study the relationships between individual is social network analysis (SNA). A social network contains a set of actors and a set of relationships connecting these actors, which could be groups, organizations or persons. SNA can quantify, visualize, and statistically test hypotheses of the relationships between actors to examine the structure of network and major factors that affect the structure of the network [@Freeman2004; @Salvini2010]. To be specific, actors are "nodes" in a wider network, in which nodes are connected by multiple relationships, or "edges", to other nodes [@Coward2013; @Mizoguchi2013; @Potgieter2008]. Relationships can be viewed as flows of resources that reflect relations of control, dependence, and cooperation, reflecting social relation in a given society.

<!--archaeology case-->
The archaeological sites in northeastern Taiwan show some evidence of accumulation of imported prestige goods in burials around the same time as European contact in the 17th century[@Chen2007], which might indicate the pursuit of prestige or wealth in the society. In addition to prestige, European colonial powers could have provided military support to indigenous allies. For example, @Voss2005's study of a colonial outpost in California shows that colonial residents have different identities and higher social status than other local indigenous people. A general model to summarize these case studies might be that the support of a colonial power combined with high local values for imported goods, might lead to competition among individuals. In this study, we will use this model of competition to explain the changes in social inequality at Kiwulan, an Iron Age site in northesatern Taiwan, which covers the presence of the Europeans, including the Spanish and the Dutch, in the 17th century and the Chinese in the 19th century.

>>>>

<!--burial study- network analysis-->
Burials provide valuable information about past human behavior that can reflect not only the personal life and status of the deceased, but also the expressions of their descendants through grave goods and arrangements [@Pearson1999]. Mortuary practices such as burial forms, grave goods, and related ritual practices could represent the social relations between individuals and allow archaeologists to infer social structures. This enables the study of social differences based on burials to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For examples, the use of burial goods can reflect social practices in a broader of cultural contexts to present personal wealth, social roles, or a traditional custom. Burials with grave goods in common often indicates underlying social relation connected through trade, exchange, and gifting [@Coward2013, pp. 252]. Identifying the structure of relationships among burials allows a further inferences on a structure of a social organization. One way to study relationships between individuals is social network analysis (SNA). A social network contains a set of actors and a set of relationships connecting these actors, which could be groups, organizations or persons. SNA can quantify, visualize, and statistically test hypotheses of the relationships between actors to examine the structure of network and major factors that affect the structure of the network [@Freeman2004; @Salvini2010]. To be specific, actors are "nodes" in a wider network, in which nodes are connected by multiple relationships, or "edges", to other nodes [@Coward2013; @Mizoguchi2013; @Potgieter2008]. Relationships can be viewed as flows of resources that reflect relations of control, dependence, and cooperation, reflecting social relation in a given society.

<!--archaeology case-->
The archaeological sites in northeastern Taiwan show some evidence of accumulation of imported prestige goods in burials around the same time as European contact in the 17th century [@Chen2007], which might indicate the pursuit of prestige or wealth in the society. In addition to prestige, European colonial powers could have provided military support to indigenous allies. For example, @Voss2005's study of a colonial outpost in California shows that colonial residents have different identities and higher social status than other local indigenous people. A general model to summarize these case studies might be that the support of a colonial power combined with high local values for imported goods, might lead to competition among individuals. In this study, we will use this model of competition to explain the changes in social inequality at Kiwulan, an Iron Age site in northesatern Taiwan, which covers the presence of the Europeans, including the Spanish and the Dutch, in the 17th century and the Chinese in the 19th century.
